Master thesis

### 2017-05-30 index.Rmd
wip

# Preface {-}

@@

This is the online html version of my master thesis. The pdf version is available for download with the download button on top of the windows.

Have a nice reading.

<div align="right">  *Sylvain*

>>>>

`r if (knitr:::is_html_output()) '# Preface {-}'`

`r if (knitr:::is_html_output()) '![stability-wip](https://img.shields.io/badge/stability-work_in_progress-lightgrey.svg)'`

@@

`r if (knitr:::is_html_output()) 'This is the online html version of my master thesis. The pdf version is available for download with the download button on top of the windows.'`

`r if (knitr:::is_html_output()) 'Have a nice reading.'`

`r if (knitr:::is_html_output()) '<div align="right">  *Sylvain*'`
